### 2023-12-13 sections/4-results.tex
added TODO

\caption{Algorithm performance across four datasets. In each plot, the horizontal axis represents increasing cardinality (size) of the dataset, while the vertical axis represents the throughput in queries per second (higher is better).}
\end{figure}

>>>>

\caption{Algorithm performance across four datasets. In each plot, the horizontal axis represents increasing cardinality (size) of the dataset, while the vertical axis represents the throughput in queries per second (higher is better). TODO say something about plots that didn't finish.}
\end{figure}
